%-------------------------
% Resume in Latex
% Author : Timothy  Faniran
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://www.linkedin.com/in/timothy-faniran/}{\Large Timothy Faniran}} & Email : \href{mailto:tim.faniran@gmail.com}{tim.faniran@gmail.com}\\
  \href{http://www.linkedin.com/in/timothy-faniran/}{http://www.linkedin.com/in/timothy-faniran} & Mobile : +1-301-747-8042 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Prairie View A and M University}{Prairie View, TX}
      {Master of Science in Computer Information Systems;  GPA: 4.00}{2017 -- 2019}
     \resumeSubheading
      {Obafemi Awolowo University}{Ile-Ife, Nigeria}
      {Masters in Tests and Measurement; Distinction}{2015 -- 2017}
    \resumeSubheading
      {Obafemi Awolowo University}{Ile-Ife, Nigeria}
      {Bachelor of Science in Mathematics}{2008 -- 2012}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages and Technology}
      {Python (Scikit-learn, NumPy, Pandas, Tensorflow, Keras, PyMongo), SQL, Javascript (React, Angular), CSS, HTML, Hadoop.}
    \resumeSubItem{Data Analytics and Visualization Tools}
      {Tableau, PowerBI, SAS, R, SPSS, MATLAB.}
    \resumeSubItem{Machine Learning and Statistical Analysis}
      {Regression Analysis, Correlation, Classification, Feature Engineering, Data Scraping, Confidence Interval.}
      \resumeSubItem{Charting Libraries and tools}
      {D3, Highcharts, Charts, Plotly, Matplotlib, Seaborn.}
    \resumeSubHeadingListEnd

%
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Prairie View A and M University}{Prairie View, TX}
      {Graduate Research Assistant}{2017 - Present}
      \resumeItemListStart
%         \resumeItem{Tensorflow}
%           {TensorFlow is an open source software library for numerical computation using data flow graphs; primarily used for training deep learning models.}
        \resumeItem{Web Development}
          {Improved Study Abroad participation through the development and integration of a Web-based Software for Prairie View University's Study Abroad Program.}
\resumeItem{Data Collection and Analysis}
          {Conducted Survey and analyzed data to optimize International Initiatives within the University.}
      \resumeItemListEnd

    \resumeSubheading
      {Visa, Inc.}{Foster City, CA}
      {Software Engineering Intern}{Summer 2018}
      \resumeItemListStart
      \resumeItem{Data Visualization Dashboard}
          {Designed a real-time dashboard that displays key business metrics formatted in easily readable manner using React/D3 with a working knowledge of Web Technologies like HTTP, HTML/DOM, JS, CSS, AJAX.}
          \resumeItem{Data Manager Security}
          {Maintained the sanctity of the data manager by using a NoSQL database as a distributed database to store data injected from the data manager for access by the API calls.}
        \resumeItem{Reports and Recommendations}
          {Generated reports and recommendations based on data analysis to provide decision support functionalities.}
          \resumeItem{Data Analytics and Insight Generation}
          {Generated Natural Language Processed Statements that present further data insights from business metrics.}
          \resumeItem{Lambda Architecture}
          {Used Lambda Architecture to fetch batch and real time data into the NoSQL database.}
        \resumeItem{API Development}
          {Developed APIs for automatic data querying and transmission to aid data visualization.}
      \resumeItemListEnd

    \resumeSubheading
      {Paradime Edge}{Lagos, NG}
      {Software Engineer/Data Scientist}{2014 -- 2017}
      \resumeItemListStart
        \resumeItem{Web Development}
          {Developed a web application for managing event management vendors using HTML/CSS/JS/MySQL.}
        \resumeItem{Data Scraping, Cleaning and Analysis}
          {Identified, analyzed and interpreted trends and patterns for large complex datasets using statistical techniques.}
          \resumeItem{Data Collection Optimization}
          {Optimized data collection procedures and generated reports on a weekly, monthly and quarterly basis.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Data Visualization Tool}
      {Designed a data visualization tool that present most commonly used business metrics for application stakeholders for easy accessibility to data/information in a near real time technique using React and D3.}
    \resumeSubItem{Statistical Prediction and Modeling}
      {Predicted learning outcomes of High School Students in Mathematics concepts based on their learning patterns using Regression Analysis.}
    \resumeSubItem{Data Mining}
      {Developed a data mining model that enhanced market segmentation through the description of customer attributes and characteristics.}
    \resumeSubHeadingListEnd

%
%-------------------------------------------
\end{document}